Practical Considerations for Lomb-Scargle Periodic Analysis

### 2016-12-08 paper.tex
Finish discussion of Fourier pairs

@@

   \item[A time-shift imparts a phase in the Fourier transform.]
     That is for any function $g(t)$,
     \begin{equation}
       \mathcal{F}\{g(t - t_0)\} = e^{-2\pi i ft_0}\mathcal{F}\{g(t)\}
     \end{equation}
     The key observation here is that the time-shift does not change the
     amplitude of the result, but only the phase.
\end{description}

There are a couple useful consequences of these properties.

...

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{fig03_Fourier_pairs}
\caption{Visualization of important Fourier pairs.}
\end{figure}

Dirac comb
\begin{equation}
    C(t, \Delta t) = \sum_{k=-\infty}^\infty \delta(t - k\Delta t)
\end{equation}
Fourier transform is
\begin{equation}
    \mathcal{F}\{C(t, \Delta t)\} = \frac{1}{\Delta t} C(f, 1/\Delta t)
\end{equation}

Tophat and Sinc
\begin{equation}
  tophat(t; T) \equiv \left\{
  \begin{array}{ll}
    1 / T & {\rm if}\ |t| < T / 2 \\
    0     & {\rm otherwise}
  \end{array}
  \right.
\end{equation}
Fourier transform is
\begin{equation}
  sinc(t) \equiv \frac{\sin(\pi t)}{\pi t}
\end{equation}

Gaussian

\begin{itemize}
  \item Chart of Fourier pairs
\end{itemize}

>>>>

\usepackage{amsmath}
\DeclareMathOperator{\sinc}{sinc}
\DeclareMathOperator{\III}{III}

@@

   \item[A time-shift imparts a phase in the Fourier transform.]
     In other words, for any well-behaved function $g(t)$ we can write
     \begin{equation}
       \mathcal{F}\{g(t - t_0)\} = \mathcal{F}\{g(t)\} e^{-2\pi i ft_0}
     \end{equation}
     The key observation here is that the time-shift does not change the
     amplitude of the resulting transform, but only the phase.
\end{description}

These properties taken together make the Fourier transform quite useful for the study of periodic signals.
The linearity of the transform means that any signal made up of a sum of periodic components will have a Fourier transform consisting of a sum of delta functions at those frequencies: that is, the Fourier transform is a {\it direct} measure of the periodic content of a function.

Further, if we compute the squared amplitude of the resulting transform, we can both do away with complex components and remove the phase imparted by any time offsets; this squared amplitude is usually known as the {\it Power Spectrum}:
\begin{equation}
  \mathcal{P}\{g\} \equiv \left|\mathcal{F}\{g\}\right|^2
\end{equation}
The power spectrum of a function is a positive real-valued function of $f$ that quantifies the contribution of each frequency $f$ to the total signal.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{fig03_Fourier_pairs}
\caption{Visualization of important Fourier pairs.\figlabel{fourier_pairs}}
\end{figure}

We have already discussed that the Fourier transform of a complex exponential is a single delta function.
This is just one of many ``Fourier Pairs'' to keep in mind as we progress to understanding the Lomb-Scargle Periodogram.
We list a few more important pairs here (see \Fig{fourier_pairs} for a visual representation of the following pairs):

\begin{description}
  \item[The Fourier transform of a sinusoid is a pair of Delta functions.]
    \begin{equation}
      \mathcal{F}\{\cos(2\pi f_0 t)\} = \frac{1}{2}\left[\delta(f-f_0) + \delta(f+f_0)\right]
    \end{equation}
    We saw this above, but repeat it here for completeness.

   \item[The Fourier transform of a Gaussian is a Gaussian.]
     \begin{equation}
       \mathcal{F}\{{\rm N}(t; \sigma)\} = \frac{1}{\sqrt{2\pi\sigma^2}}{\rm N}\left(f;\frac{1}{2\pi\sigma}\right)
     \end{equation}
     The Gaussian function ${\rm N}(t, \sigma)$ is given by
     \begin{equation}
       {\rm N}(t; \sigma) \equiv \frac{1}{\sqrt{2\pi\sigma^2}}e^{-t^2 / (2\sigma^2)}
     \end{equation}

  \item[The Fourier transform of a tophat function is a sinc function.]
    \begin{equation}
      \mathcal{F}\{\Pi_T(t)\} = \sinc(f T)
    \end{equation}
    The tophat function, $\Pi_T(t)$ is a normalized symmetric function that
    is uniform within a range given by $T$, and zero elsewhere:
    \begin{equation}
      \Pi_T(t)  \equiv \left\{
      \begin{array}{ll}
        1 / T, & |t| \le T / 2 \\
        0,     & |t| > T / 2
      \end{array}
      \right.
    \end{equation}
    The sinc function is given by the standard definition:
    \begin{equation}
      \sinc(x) \equiv \frac{\sin(\pi x)}{\pi x}
    \end{equation}

  \item[The Fourier transform of a Dirac comb is a Dirac comb.]
    \begin{equation}
      \mathcal{F}\{\III_T(t)\} = \frac{1}{T}\III_{1/T}(f)
    \end{equation}
    The Dirac comb $\III_T(t)$ is an infinite sequence of Dirac delta functions
    placed at even intervals of size $T$:
    \begin{equation}
      \III_T(t) \equiv \sum_{k=-\infty}^\infty \delta(t - kT)
    \end{equation}
\end{description}

The key observation in each of these is the reciprocity of scales across the
Fourier transform: a function with a characteristic scale $T$ will generally
have a Fourier transform with characteristic scale proportional to $1/T$.
This feature will turn out to be very important as we push further in
understanding the Lomb-Scargle Periodogram.
